Technique for \earlywarning\ detection of compact binary coalescence and its implications for multi-messenger astronomy

### 2011-06-03 conclusions.tex
changed future plan discussion
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@929 ccdd05d5-56c1-461a-bf98-85f6876523b4

\editorial{We should drive home the point that our method is as fast as the fft convolution but without any latency at all.}%
We have demonstrated a computationally feasible procedure for the rapid and even preemptive
detection of gravitational waves emitted during the coalescence of neutron
stars and stellar-mass black holes. Our method is as fast as standard \fft{}
convolutions but without any latency at all. Our search targets are expected to
produce prompt electromagnetic signals and may be the progenitors of some short
hard gamma-ray bursts.  Rapid alerts to the broader astronomical community will
improve the chances of detecting an electromagnetic counterpart in bands from
gamma-rays down to radio.  We anticipate requiring $\sim$\numcpus\ modern
%
\editorial{We need to do this calculation using the \flops\ counts and the
number of templates. CHAD: Agreed, but if you do it by the books it seems
misleading.  I have adjusted it to 600.  This number is taken from assuming
that 1 657 template sub-bank can be filtered on one core and dividing the total
number of templates (10$^5$) by 657 which gives you 150 cores per detector. I
put it in section 2. }%
%
computer cores to analyze a four-detector network of gravitational-wave data
for binary neutron stars and stellar-mass black holes.  This is well within the
current computing capabilities of the \textsc{lsc} Data Grid~\cite{LDG}.

@@

\editorial{The way this is worded, it sounds like a big omission.}%
We have omitted discussion of source localization though point
the reader to some theoretical estimates \SNR~\cite{Fairhurst2009}.
%However, one should not immediately dismiss the practical usefulness of a
%poorly localized source. Even with poor localization, it should be possible to
%begin downselecting what observatories could view a potential signal and for
%such observatories to begin any necessary prerequisite activities. 
In future works we will explore more rigorously the pointing prospects with
realistic simulations using the infrastructure and techniques described here.
\editorial{nvf: It's a bit pie-in-the-sky, but we could also mention reconfiguring
the signal recycling mirror to optimize SNR at merger. There's a lot of science there.}

>>>>

\editorial{We should drive home the point that our method is as fast as the fft convolution but without any latency at all.}%
We have demonstrated a computationally feasible procedure for the rapid and even preemptive
detection of gravitational waves emitted during the coalescence of neutron
stars and stellar-mass black holes. Our method is as fast as standard \fft{}
convolutions but without any latency at all. Our search targets are expected to
produce prompt electromagnetic signals and may be the progenitors of some short
hard gamma-ray bursts.  Rapid alerts to the broader astronomical community will
improve the chances of detecting an electromagnetic counterpart in bands from
gamma-rays down to radio.  We anticipate requiring $\sim10\times4$ modern
multi-core computers to analyze a four-detector network of gravitational-wave data
for binary neutron stars and stellar-mass black holes.  This is well within the
current computing capabilities of the \textsc{lsc} Data Grid~\cite{LDG}.

@@

We plan to explore more rigorously the prospects of early warning detection
with realistic simulations of binary mergers using the infrastructure and
techniques described here.  We will compare the performance of the early
warning pipeline sky localization capabilities with the theoretical
estimates~\cite{Fairhurst2009}.

\editorial{nvf: It's a bit pie-in-the-sky, but we could also mention reconfiguring
the signal recycling mirror to optimize SNR at merger. There's a lot of science there.}
